Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-12 paper/main.tex
Added fraction to hashing time tables and updated conclusions

The third column in Tables \ref{tbl:hashingtimes:put1gb} and
\ref{tbl:hashingtimes:get1gb} contains the time spent doing other operations
than hashing, i.e. $Total time - Time spent hashing$. This number varies
between 227.37s and 252.66s during upload and 205.94s and 225.03s during
download.

@@

\section{\ac{SUPERCOP} results}
% Time gain of removing ``double'' SHA-256. Double only in digest().

@@

\section{Validity of \ac{SUPERCOP} results}
% Mention that some SUPERCOP candidates are missing UPDATE-functionality.

@@

\section{Exclusion of mutable file testing}
% Implications of only testing immutable files? (mutable files also
%   include directories)
% Adding a capability to support new hash functions in tahoe. (Our
%   current way breaks backwards compatibility)

@@

\subsection{The use of Cython}
% What if we had used another coding scheme? - does Cython lower the
%   candidates performance?

@@

\subsection{Faster implementations}
We do not claim to have tested the fastest possible nor existing version
of most of the candidates. We are certain that someone of more skill and
knolwedge about the inner workings of the \ac{SHA}-3 candidates, \ac{GCC} and
Python could make significantly faster implementation.

@@

We had hoped to contribute more to the Open Source project Tahoe-LAFS, when
starting on our assignment. It was early evident that implementing a new
capability was out of scope, since creating Python bindings for and trying out
new implementations was prioritized.

>>>>

The third column in Tables \ref{tbl:hashingtimes:put1gb} and
\ref{tbl:hashingtimes:get1gb} contains the time spent doing other operations
than hashing, i.e. $Total time - Time spent hashing$. This number varies
between 227.37s and 252.66s during upload and 205.94s and 225.03s during
download. \emph{Fraction} displays the part of total time the calls to the
hashing libraries take.

@@

\section{\ac{SUPERCOP} results}

@@

\section{Validity of \ac{SUPERCOP} results}

@@

\section{Exclusion of mutable file testing}

@@

\subsection{The use of Cython}

@@

\subsection{Faster implementations}
We do not claim to have tested the fastest possible nor existing version
of most of the candidates. We are certain that someone of more skill and
knowledge about the inner workings of the \ac{SHA}-3 candidates, \ac{GCC} and
Python could make significantly faster implementation.

@@

We had hoped to contribute more to the Open Source project Tahoe-LAFS, when
starting on our assignment. It was early evident that implementing a new
capability was out of scope, since creating Python bindings and trying out
new implementations was prioritized.

Four of the candidates has been shown to perform better than the currently used
SHA-256 -- BLAKE, BlueMidnightWish, Shabal and Simd. The time it takes for
Tahoe-LAFS to upload a one gigabyte file, could improve by $5\%$ if the best
performing SHA-3 candidate, BLAKE, were to be used.
